Analysis-ready VCF at Biobank-scale using Zarr

### 2024-05-08 paper.tex
some notes on hardware

>>>>

All simulation-based benchmarks were performed on a 
dual CPU (Intel Xeon E5-2680 v2)
server with 256GiB of RAM running Debian GNU/Linux 11.
To ensure that the true effects of having data distributed over a large 
number of files were reported, benchmarks for Zarr and Savvy were 
performed on a cold disk cache by running 
\texttt{echo 3 | sudo tee /proc/sys/vm/drop\_caches} before each run.
The IO subsytem used is based on a RAID 5 of 12 SATA hard drives.
